---
title: "Try4_with_stepAIC_RF_Plot"
author: "Linxiao Bai"
date: "2/11/2017"
output: html_document
---
###Loading Packages
```{r results='hide', message=FALSE, warning=FALSE}
library(nnet)
library(MASS)
library(randomForest)
```
###Loading data with all r data as training, and test from python
```{r}
load('/Users/Pagliacci/Desktop/DSC450/samsungData.rda')
colnames(samsungData) = make.names(names(samsungData), unique = TRUE)
samsungData$activity=as.factor(samsungData$activity)

new_test = read.csv('/Users/Pagliacci/Desktop/DSC450/X_test.csv',header=FALSE)
names(new_test) = names(samsungData)[1:561]

new_test_y=read.csv('/Users/Pagliacci/Desktop/DSC450/y_test.csv', header = FALSE)
new_test_y[new_test_y == 1] = 'walk'
new_test_y[new_test_y == 2] = 'walkup'
new_test_y[new_test_y == 3] = 'walkdown'
new_test_y[new_test_y == 4] = 'sitting'
new_test_y[new_test_y == 5] = 'standing'
new_test_y[new_test_y == 6] = 'laying'
new_test$activity=as.factor(new_test_y$V1)

train=samsungData
test=new_test

```
###Forward AIC selection with Multinomial Logistic
```{r results='hide', message=FALSE, warning=FALSE}
fml_full=formula(paste("activity~",paste(colnames(train)[1:ncol(train)-1],collapse="+")))
step_result=step(multinom(activity~1,data=train,trace=0),
                 scope=fml_full,direction='forward',steps=7,trace=FALSE)
```
###Plot AIC decrease trend against the number of predictors.
```{r}
plot(x=0:7,y=step_result$anova$AIC,type = "b",xlab = "Number of Predictors", ylab="AIC",main="Forward Selection AIC")
```
###Test performance on test data according to the number of predictors
```{r}
accuracy=list()
for(i in 2:8){
  fml=formula(paste("activity~",paste(step_result$coefnames[2:i],collapse="+")))
  rfmdl=randomForest(fml,data=train,trace=0)
  accuracy=c(accuracy,mean(predict(rfmdl,newdata=test)==test$activity))
}

data.frame("Step"=step_result$anova$Step[2:8],"accuracy"=unlist(accuracy))
plot(x=1:7,y=unlist(accuracy),type="b",ylab="Test Accuracy",xlab="Number of Predictors")
```
###The AIC curve shows significant decrease of AIC before 4 predictors, might be a good idea to choose 4, where we have over 80% accuracy, and also not too many predictors. The follwing result gives detail about the goodness of fit of our final model.
```{r}
RFfml4=formula(paste("activity~",paste(step_result$coefnames[2:5], collapse ="+")))
RFfml4
RFmdl4=randomForest(RFfml4,data=train)
table(predict(RFmdl4,newdata=test),test$activity)
mean(predict(RFmdl4,newdata=test)==test$activity)
```

